### 2017-04-10 paper/oopsla17-submission/conclusion.tex
small conclusion

>>>>

We have presented a new data-driven approach to localizing type errors,
using machine learning to assign blame based on previously seen novice
mistakes.
%
We translate ill-typed programs into sets of feature vectors, predict
for each sub-expression whether it should be blamed, rank the
predictions based on the model's confidence, and select the top three
blame assignments to present to the user.
%
We represent expressions solely by their syntactic class and type, and
those of their parent and children.
%
We have evaluated our approach with five different learning algorithms
on a suite of over 4,500 student programs, and found that all of our
models outperform the state of the art, by up to a 16\% margin.
%

### 2017-04-10 paper/oopsla17-submission/introduction.tex
small conclusion

Type systems are one of the most widely-used techniques for program
verification. A type checker only accepts a program if it can
\emph{prove} the absence of an entire class of bugs.
%
Typed functional languages like \ocaml and \haskell are equipped with
particularly powerful type checkers that can operate without a single
annotation, alleviating a prime concern with verification techniques.
%
Yet this power comes with a cost: since type annotations signify the
programmer's \emph{intent}, without them the checker must
make assumptions about what the programmer intended to do.
%
This results in the common phenomenon of type errors being reported far
from their source, an annoyance to veterans of the type system, but a
major hurdle for novices \citep{Wand1986-nw,Joosten1993-yx}.

>>>>

Type systems are one of the most widely-used techniques for program
verification. A type checker only accepts a program if it can
\emph{prove} the absence of an entire class of bugs.
%
Typed functional languages like \ocaml and \haskell are equipped with
particularly powerful type checkers that can operate without a single
annotation, alleviating a prime concern with verification techniques.
%
Yet this power comes with a cost: type annotations signify the
programmer's \emph{intent}, without them the checker must
make assumptions about what the programmer intended to do.
%
This results in the common phenomenon of type errors being reported far
from their source, an annoyance to veterans of the type system, but a
significant hurdle for novices \citep{Wand1986-nw,Joosten1993-yx}.
